### 2018-04-18 concepts.tex
new draft, text

The probability that this test behaves nondeterministically is
0.84645, the result of the simple calculation $(1-0.01) \times
(1-0.05) \times (1-0.10)$.  Figure \ref{fig:p1} shows one run of
delta-debugging on a test of length 500.  The initial test is
esentially guaranteed to behave nondeterministically; delta-debugging
only checks that it \emph{can} behave nondeterministically, and so, in
the course of reducing the test length to a test with only two
operations, the delta-debugging algorithm also reduces the probability
of nondeterminism to only about 20\%.  If we use a predicate that
``forces'' the test to behave nondeterministically at least half the
time, by sampling the predicate value 100 times and only returning
true when at least 50 of the evaluations report true, we see the
behavior in Figure \ref{fig:p2}:  the final test is slightly longer,
but still falls well short of our target of exhibiting nondeterminism
50\% of the time.  Finally, Figure \ref{fig:p3} shows what happens if
we use the same target of 50\% nondeterminism, but use only 10
samples, with 10 replications ($N$ = 10, $M$ = 10):  the test is not
much longer than in Figure \ref{fig:p2}, but the probability of
nondeterminism is above our target value, close to 60\%.  Note that
this example is purely monotonic; the pattern of probability changes
in non-monotonic settings can be even more difficult to predict and
control, but the principle of forcing a probability by sampling and
replication still holds.

>>>>

The probability that this test behaves nondeterministically is
0.84645, the result of the simple calculation $(1-0.01) \times
(1-0.05) \times (1-0.10)$.  Figure \ref{fig:p1} shows one run of
delta-debugging on a test of length 500.  The initial test is
esentially guaranteed to behave nondeterministically; delta-debugging
only checks that it \emph{can} behave nondeterministically, and so, in
the course of reducing the test length to a test with only two
operations, the delta-debugging algorithm also reduces the probability
of nondeterminism to only about 20\%.  If we use a predicate that
``forces'' the test to behave nondeterministically at least half the
time, by sampling the predicate value 100 times and only returning
true when at least 50 of the evaluations report true, we see the
behavior in Figure \ref{fig:p2}:  the final test is slightly longer,
but still falls well short of our target of exhibiting nondeterminism
50\% of the time.  Finally, Figure \ref{fig:p3} shows what happens if
we use the same target of 50\% nondeterminism, but use only 10
samples, with 10 replications ($N$ = 10, $M$ = 10):  the test is not
much longer than in Figure \ref{fig:p2}, but the probability of
nondeterminism is above our target value, close to 60\% (and, as a bonus, fewer
test executions are required on average for each check of the predicate).  Note that
this example is purely monotonic; the pattern of probability changes
in non-monotonic settings can be even more difficult to predict and
control, but the principle of forcing a probability by sampling and
replication still holds.

### 2018-04-18 implementation.tex
new draft, text

 Tables \ref{tab:methods}
and \ref{tab:options} show, respectively, the primary additions to the
TSTL Python API and the TSTL command line tools.  The TSTL test
generation tool is called {\tt rt}, since the default mode is a fast
pure Random Tester, and {\tt reduce} is TSTL's tool for
delta-debugging and test
normalization (more aggressive reduction that also tends to ease
debugging and test triage by making tests failing due to the same
fault more similar \cite{onetest}).  With these additions,
developers of TSTL-based testing tools, or developers using TSTL tools
to test code can easily add nondeterminism to the set of properties
checked.

>>>>

 Tables \ref{tab:methods}
and \ref{tab:options} show, respectively, the primary additions to the
TSTL Python API and the TSTL command line tools.  The TSTL test
generation tool is called {\tt rt}, since the default mode is a fast
pure Random Tester, and {\tt reduce} is TSTL's tool for
delta-debugging and test
normalization (more aggressive reduction that also tends to ease
debugging and test triage by making tests failing due to the same
fault more similar \cite{onetest}).  With these additions,
developers of TSTL-based testing tools, or developers using TSTL tools
to test code can easily add nondeterminism to the set of properties
checked.  It is even possible to write a TSTL harness that
automatically checks itself for nondeterminism, even if the random
tester is not run with {\tt --checkDeterminism}, simply by adding:

{\scriptsize
\begin{code}
property: not self.nondeterministic(self.test())
\end{code}
}

\noindent to the harness; in fact, by removing the {\tt not}, a test harness can
even specify that behavior should not be deterministic, a property of
possible use in some security-related libraries.
